\section{21st of November, 2011}
\subsection{Meeting structure}
Finished our meeting structure: \\
\subsubsection{Before meetings}
\paragraph{BeforePerson}
standing up
\begin{itemize}
\item What I have done since last time
\item What do I want to get done today?
\item What can prevent me from doing that?
\item Special requests etc.
\end{itemize}
\paragraph{BeforeGroup}
\begin{itemize}
\item How are we doing considering our weekly plan?
\item What do we need to do today?
\item Agreements, etc.
\item When do we have lunch?
\item When do we end today?
\end{itemize}

\subsubsection{Lunchtime}
Evaluate very quickly just after lunch - let people finish eating and request help etc.

\subsubsection{After the meeting} 
End 15 minutes before 'end time'
\paragraph{AfterPerson}
\begin{itemize}
\item Go through the day
\item Special requests in terms of planning etc.
\end{itemize}

\paragraph{AfterGroup}
\begin{itemize}
\item Next meeting
\item Possible election of next 'meeting leader'
\item Homework
\end{itemize}

\paragraph{Last day of 'week'} 
Another 15 to 20 minutes before end time
\begin{itemize}
\item Summary of week
\item Did we do what we planned?
\item Plan for the next week
\end{itemize}

\subsection{Summary of today}
\subsubsection{Next meeting}
\begin{itemize}
\item Day: 23rd of November, 2011
\item Time: About 10, 100\% serious from 11
\item At IT-University
\item Room should have a whiteboard
\end{itemize}

\subsubsection{Homework}
\paragraph{Jakob Melnyk}
BON for gamestate, etc. \& have an idea of how the BON for the 'behind the scenes' classes should look like in BON
\paragraph{Frederik Lysgaard}
Look more at XNA \& consider some BON for the GUI
\paragraph{Christian Jensen}
BON for cards, rules, etc. \& think about how to implement 'weird rules'