\section{3rd of December}
\subsection{How are we doing with this weeks plan?}
\begin{itemize}
\item  Frederik doing good - working on GUI mockup
\item Melnyk: Almost there
\item Christian: A bit behind, but will work extra hard to make it on time.
\end{itemize}

\subsection{What do we need to do today?}
\begin{itemize}
\item Frederik: Mock-ups
\item Christian: Try to get 2 clients and server to work.
\item Jakob: Finish flow-diagram of real Dominion game and do a lot of work on gamestate BON
\end{itemize}

\subsection{Agreements}
\begin{itemize}
\item Skip meeting Sunday 3rd
\item Test by playing game when it is possible
\item Think up scenarios for hand-written tests
\end{itemize}
\subsection{Lunch and end times}
Lunch:
13.00-13.30
End:
17.00
\subsection{End of meeting}
Summary of the day:

Frederik: Looked at XNA and really got into it. Did paper mockups.

Jakob: Finished flow diagram of a real Dominion game and got started on gamestate.

Christian: Did some server stuff, stll a few problems. No BON yet.
\subsubsection{Next meeting}
Monday 5th, 11.00

Homework:

Frederik: Look at XNA listeners

Christian: Get server stuff done and get BON ready.

Jakob: Finish Gamestate BON and finish Card BON. Start on flow diagram of application. Get overview of stuff from Troy.
\subsubsection{End of Week}
Summary: We really got started on BON and networking. Frederik got quite far with the GUI. Jakob made a flow diagram and Christian is pretty into the networking stuff.

Did what we planned?: 

Frederik: Accomplished what he set out to do, except for the more visual part.

Jakob: Should have been further with the BON, really needs to catch up on that. Want to start formal BON before next week if possible

Next week meeting days: Mandag, onsdag, fredag, lørdag, søndag