\section{11th of December}
\subsection{How are we doing with this weeks plan?}
\begin{itemize}
\item Frederik: Doing REAL GOOD.
\item Jakob: Will not be at 95\% and will not really have tests, but should be close.
\end{itemize}

\subsection{What do we need to do today?}
\begin{itemize}
\item Jakob: Gamestate code en masse.
\item Frederik: Make first real version of GUI.
\item Christian:Interface for the server
\end{itemize}

%\subsection{Agreements}
%\begin{itemize}
%\item 
%\end{itemize}
\subsection{Lunch and end times}
Lunch:
13.00-13.30
End:
TBD
\subsection{End of meeting}
Christian: Did interface for the network, have not really tested, but feels good.

Frederik: Progress on the GUI - deck, hand, discard, action zones are now believed to be working as intended. Supply just around the corner.

Jakob: Slowly getting gamestate up and going - need to talk to Joe about contracts.

Homework: 

Christian: None.

Frederik: Really wants to get supply drawn.

Jakob: Wants to finish Player and everything except Gamestate. Get started on Gamestate.
\subsubsection{Next meeting}
Monday12th 11.00 at ITU
\subsubsection{End of Week}
Jakobs part is pretty delayed due to hospital stuff. Christian feels he has done what he needed to do. Network seems pretty solid.

Frederik:  If Supply is done for monday, then he has done what he felt he needed to get done.

Plan:

Monday: Go through what we still need to code. Basic code needs to be done - not including tests - around evening. Aim is to be done pretty much done with coding by Monday night, so we can test "extensively" Tuesday.

Tuesday: Do testing and make sure we have everything possible covered in terms of the actual hand-in.

Wednesday: Pretty much just hand-in the project early in the morning, if possible.

Do close to hourly meetings, so we are clear on how everyone is doing. Stay late Tuesday if neccesary to make sure we have something to hand-in early.